Report on the Second Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE2)

### 2015-03-19 WSSSPE2_report/WSSSPE2_review.tex
Section 2: touch up.

\item recommendations for the support and maintenance of existing software
\begin{itemize}
\item software engineering best practices
\item governance, business, and sustainability models
\item the role of community software repositories, their operation and
sustainability
\item reproducibility, transparency needs that may be unique to science
\end{itemize}

@@

The review process was fairly standard, where reviewers bid for papers, then an
automated system
matched bids to determine assignments, and reviewers then completed their
assigned
reviews (with an average of 4.9 reviews per paper, and 4.1 reviews per
reviewer).
This process was done through EasyChair\footnote{http://easychair.org/}, which
allowed reviewers to provide scores on relevance and comments to the organizers,
which were used to decide which papers to associate with the workshop, and
comments to the authors, which were provided back to the authors to allow them
to improve their papers.

@@

For WSSSPE2, the organizers wanted to increase the interactivity of the
sessions, and to open the process of creating the sessions to the full program
committee, the paper authors, and others who might attend the workshop. In order
to do this, the organizers decided to use a breakout format for two sessions,
and to use an open process to determine the breakout topics. Specifically,
well-sorted\footnote{\url{http://www.well-sorted.org}} was used as follows:
\begin{enumerate}
\item Authors were asked to create well-sorted ``cards'' for the papers. These
cards have a title (50 characters maximum) and a body (255 characters maximum).
\item Authors, program committee members, and members of the WSSSPE mailing list
were asked to sort the cards. Each person drags the cards, one by one, into
groups. A group can have as many cards as the person wants it to have, and it
can have whatever meaning makes sense to that person.
\item Well-sorted then produces a set of averages of all the sorts, with various
numbers of clusters of cards.
\end{enumerate}

The organizers then chose the sort that contained five groups as the one that
felt most meaningful, then decided on names for the five groups, namely:
\begin{itemize}
\item Exploring Sustainability
\item Software Development Experiences
\item Credit \& Incentives
\item Reproducibility \& Reuse \& Sharing
\item Code Testing \& Code Review
\end{itemize}

Finally, since some of the papers were not represented by cards in the process,
they were not placed in groups by the peer-grouping system, so the authors of
these papers were asked which group seemed the best for their papers, and those
papers were then placed in those groups. Sections~\ref{sec:exploring}-\ref{sec:code_testing}
discuss the breakout groups, including a list of the papers associated with each
group.

>>>>

\item recommendations for the support and maintenance of existing software
\begin{itemize}
\item software engineering best practices
\item governance, business, and sustainability models
\item the role, operation, and
sustainability of community software repositories 
\item reproducibility, transparency needs that may be unique to science
\end{itemize}

@@

The review process was fairly standard, where reviewers bid for papers, then an
automated system
matched bids to determine assignments, and reviewers then completed their
assigned
reviews (with an average of 4.9 reviews per paper, and 4.1 reviews per
reviewer).
This process was done through EasyChair\footnote{http://easychair.org/}, which
allowed reviewers to provide scores on relevance and comments to the organizers,
who used the information to decide which papers to associate with the workshop, and
provided the comments to the authors to help them improve their papers.

@@

For WSSSPE2, the organizers wanted to increase the interactivity of the
sessions, and to open the process of creating the sessions to the full program
committee, the paper authors, and others who might attend the workshop. In order
to do this, the organizers decided to use a breakout format for two sessions,
and to use an open process to determine the breakout topics. Specifically,
Well Sorted\footnote{\url{http://www.well-sorted.org}} was used in the following steps:
\begin{enumerate}
\item Authors were asked to create Well Sorted ``cards'' for the papers. These
cards have a title (50 characters maximum) and a body (255 characters maximum).
\item Authors, program committee members, and members of the WSSSPE mailing list
were asked to sort the cards. Each person drags the cards, one by one, into
groups. A group can have as many cards as the person wants it to have, and it
can have whatever meaning that makes sense to that person.
\item Well Sorted  produces a set of averages of all the sorts, with various
numbers of card clusters.
\end{enumerate}

The organizers then chose the sort that contained five groups as the one that
felt most meaningful, and decided on names for the five groups, namely:
\begin{itemize}
\item Exploring Sustainability
\item Software Development Experiences
\item Credit \& Incentives
\item Reproducibility \& Reuse \& Sharing
\item Code Testing \& Code Review.
\end{itemize}

Finally, since some of the papers were not represented by cards in the process,
they were not placed in groups by the peer-grouping system; the authors of
these papers were asked which groups seemed the best for their papers---these
papers were then placed in those groups. Sections~\ref{sec:exploring}-\ref{sec:code_testing}
discuss the breakout groups, including a list of the papers associated with each
group.
